Energy spectrum of diatomic molecules\\ in the Quantum Drude Oscillator model

### 2022-07-03 paper/main.tex
minor
Added numerical results to paper and plots

\preprint{APS/123-QED}

@@

\begin{abstract}
Abstract
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item.
%\end{description}
\end{abstract}

@@

    \begin{table}[h!]
    \caption{\label{tab:Ar-Ar} Energy spectrum (in Ha) of the Ar-Ar system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 9.247342 & 32.416619 & 62.971511 \\
        1.0 & 2.981229 & 10.350087 & 20.248422 \\
        1.5 & 1.563464 & 5.442288 & 10.069702 \\
        2.0 & 1.023301 & 3.394336 & 6.337199 \\
        2.5 & 0.748161 & 2.413177 & 4.876881 \\
        3.0 & 0.590991 & 1.960271 & 4.289340 \\  
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Cs-Cs} Energy spectrum (in Ha) of the Cs-Cs system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 4.076335 & 14.287104 & 27.755741 \\
        1.0 & 1.307214 & 4.543529 & 8.897871 \\
        1.5 & 0.673427 & 2.362932 & 4.396492 \\
        2.0 & 0.426306 & 1.441411 & 2.686432 \\
        2.5 & 0.296956 & 0.971662 & 1.957474 \\
        3.0 & 0.217699 & 0.719613 & 1.585340 \\    
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:H-H} Energy spectrum (in Ha) of the H-H system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 3.757546 & 13.234211 & 25.693826 \\
        1.0 & 1.213930 & 4.243743 & 8.293979 \\
        1.5 & 0.649664 & 2.239448 & 4.116225 \\
        2.0 & 0.436524 & 1.423565 & 2.744604 \\
        2.5 & 0.330635 & 1.081656 & 2.284054 \\
        3.0 & 0.279296 & 0.965099 & 2.204208 \\      
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:He-He} Energy spectrum (in Ha) of the He-He system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 4.838555 & 16.998352 & 32.990230 \\
        1.0 & 1.609674 & 5.563162 & 10.796479 \\
        1.5 & 0.928052 & 3.096340 & 5.617631 \\
        2.0 & 0.690066 & 2.190579 & 4.209331 \\
        2.5 & 0.597424 & 1.987363 & 4.173586 \\
        3.0 & 0.607965 & 2.159394 & 4.851867 \\       
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:K-K} Energy spectrum (in Ha) of the K-K system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 3.900846 & 13.629450 & 26.449767 \\
        1.0 & 1.254074 & 4.338725 & 8.463017 \\
        1.5 & 0.646062 & 2.260433 & 4.233126 \\
        2.0 & 0.409452 & 1.389547 & 2.556108 \\
        2.5 & 0.286775 & 0.935829 & 1.841376 \\
        3.0 & 0.211508 & 0.689674 & 1.476942 \\         
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Kr-Kr} Energy spectrum (in Ha) of the Kr-Kr system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 9.936548 & 34.839598 & 67.682787 \\
        1.0 & 3.196890 & 11.107797 & 21.743625 \\
        1.5 & 1.666467 & 5.817323 & 10.779216 \\
        2.0 & 1.078692 & 3.598874 & 6.723190 \\
        2.5 & 0.776461 & 2.514230 & 5.085759 \\
        3.0 & 0.599348 & 1.984794 & 4.360291 \\           
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Li-Li} Energy spectrum (in Ha) of the Li-Li system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 2.989579 & 10.393189 & 20.094511 \\
        1.0 & 0.965106 & 3.317199 & 6.411919 \\
        1.5 & 0.498061 & 1.728672 & 3.276409 \\
        2.0 & 0.316132 & 1.076633 & 1.951989 \\
        2.5 & 0.223280 & 0.727240 & 1.384589 \\
        3.0 & 0.166518 & 0.533844 & 1.098635 \\              
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Ne-Ne} Energy spectrum (in Ha) of the Ne-Ne system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 8.067324 & 28.257747 & 54.866835 \\
        1.0 & 2.648128 & 9.141505 & 17.802546 \\
        1.5 & 1.463214 & 4.975572 & 9.086247 \\
        2.0 & 1.037985 & 3.321372 & 6.216936 \\
        2.5 & 0.839105 & 2.707087 & 5.494303 \\
        3.0 & 0.769833 & 2.636825 & 5.742950 \\             
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Rb-Rb} Energy spectrum (in Ha) of the Rb-Rb system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 4.031874 & 14.113400 & 27.409612 \\
        1.0 & 1.294297 & 4.489885 & 8.780383 \\
        1.5 & 0.666759 & 2.337266 & 4.359340 \\
        2.0 & 0.422361 & 1.430245 & 2.650383 \\
        2.5 & 0.294937 & 0.963709 & 1.922279 \\
        3.0 & 0.216807 & 0.712417 & 1.550805 \\                
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Xe-Xe} Energy spectrum (in Ha) of the Xe-Xe system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 10.472412 & 36.762340 & 71.427248 \\
        1.0 & 3.360994 & 11.705550 & 22.941485 \\
        1.5 & 1.743863 & 6.103626 & 11.305873 \\
        2.0 & 1.117696 & 3.742926 & 7.034869 \\
        2.5 & 0.792188 & 2.580753 & 5.270133 \\
        3.0 & 0.598300 & 1.992258 & 4.438638 \\                 
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{figure}[h!]
        \centering
            \includegraphics[scale=0.33]{plus_minus_coefs}
            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$. The purple dots correspond to the first excited states of the H-H system for $r=4$ and $\mathcal E=0$.}
    \end{figure}

>>>>

%\preprint{APS/123-QED}

@@

\begin{abstract}

    We compute the energy spectrum of a system consiting of a pair of Quantum Drude Oscillators coupled through the Coulomb interaction up to Quadrupole-Quadrupole and Dipole-Octupole order in the multipolar expansion by re-expressing the Schr\"odinger equation in terms of a tri-confluent Heun equation.

\end{abstract}

@@

\subsection{First few energy levels}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Ar-Ar} Energy spectrum (in Ha) of the Ar-Ar system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 9.247342 & 32.416619 & 62.971511 \\
        1.0 & 2.981229 & 10.350087 & 20.248422 \\
        1.5 & 1.563464 & 5.442288 & 10.069702 \\
        2.0 & 1.023301 & 3.394336 & 6.337199 \\
        2.5 & 0.748161 & 2.413177 & 4.876881 \\
        3.0 & 0.590991 & 1.960271 & 4.289340 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Cs-Cs} Energy spectrum (in Ha) of the Cs-Cs system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 4.076335 & 14.287104 & 27.755741 \\
        1.0 & 1.307214 & 4.543529 & 8.897871 \\
        1.5 & 0.673427 & 2.362932 & 4.396492 \\
        2.0 & 0.426306 & 1.441411 & 2.686432 \\
        2.5 & 0.296956 & 0.971662 & 1.957474 \\
        3.0 & 0.217699 & 0.719613 & 1.585340 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_H-H} Energy spectrum (in Ha) of the H-H system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 3.757546 & 13.234211 & 25.693826 \\
        1.0 & 1.213930 & 4.243743 & 8.293979 \\
        1.5 & 0.649664 & 2.239448 & 4.116225 \\
        2.0 & 0.436524 & 1.423565 & 2.744604 \\
        2.5 & 0.330635 & 1.081656 & 2.284054 \\
        3.0 & 0.279296 & 0.965099 & 2.204208 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_He-He} Energy spectrum (in Ha) of the He-He system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 4.838555 & 16.998352 & 32.990230 \\
        1.0 & 1.609674 & 5.563162 & 10.796479 \\
        1.5 & 0.928052 & 3.096340 & 5.617631 \\
        2.0 & 0.690066 & 2.190579 & 4.209331 \\
        2.5 & 0.597424 & 1.987363 & 4.173586 \\
        3.0 & 0.607965 & 2.159394 & 4.851867 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_K-K} Energy spectrum (in Ha) of the K-K system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 3.900846 & 13.629450 & 26.449767 \\
        1.0 & 1.254074 & 4.338725 & 8.463017 \\
        1.5 & 0.646062 & 2.260433 & 4.233126 \\
        2.0 & 0.409452 & 1.389547 & 2.556108 \\
        2.5 & 0.286775 & 0.935829 & 1.841376 \\
        3.0 & 0.211508 & 0.689674 & 1.476942 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Kr-Kr} Energy spectrum (in Ha) of the Kr-Kr system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 9.936548 & 34.839598 & 67.682787 \\
        1.0 & 3.196890 & 11.107797 & 21.743625 \\
        1.5 & 1.666467 & 5.817323 & 10.779216 \\
        2.0 & 1.078692 & 3.598874 & 6.723190 \\
        2.5 & 0.776461 & 2.514230 & 5.085759 \\
        3.0 & 0.599348 & 1.984794 & 4.360291 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Li-Li} Energy spectrum (in Ha) of the Li-Li system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 2.989579 & 10.393189 & 20.094511 \\
        1.0 & 0.965106 & 3.317199 & 6.411919 \\
        1.5 & 0.498061 & 1.728672 & 3.276409 \\
        2.0 & 0.316132 & 1.076633 & 1.951989 \\
        2.5 & 0.223280 & 0.727240 & 1.384589 \\
        3.0 & 0.166518 & 0.533844 & 1.098635 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Ne-Ne} Energy spectrum (in Ha) of the Ne-Ne system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 8.067324 & 28.257747 & 54.866835 \\
        1.0 & 2.648128 & 9.141505 & 17.802546 \\
        1.5 & 1.463214 & 4.975572 & 9.086247 \\
        2.0 & 1.037985 & 3.321372 & 6.216936 \\
        2.5 & 0.839105 & 2.707087 & 5.494303 \\
        3.0 & 0.769833 & 2.636825 & 5.742950 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Rb-Rb} Energy spectrum (in Ha) of the Rb-Rb system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 4.031874 & 14.113400 & 27.409612 \\
        1.0 & 1.294297 & 4.489885 & 8.780383 \\
        1.5 & 0.666759 & 2.337266 & 4.359340 \\
        2.0 & 0.422361 & 1.430245 & 2.650383 \\
        2.5 & 0.294937 & 0.963709 & 1.922279 \\
        3.0 & 0.216807 & 0.712417 & 1.550805 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:external_field_Xe-Xe} Energy spectrum (in Ha) of the Xe-Xe system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline\\[-0.8em]
        0.5 & 10.472412 & 36.762340 & 71.427248 \\
        1.0 & 3.360994 & 11.705550 & 22.941485 \\
        1.5 & 1.743863 & 6.103626 & 11.305873 \\
        2.0 & 1.117696 & 3.742926 & 7.034869 \\
        2.5 & 0.792188 & 2.580753 & 5.270133 \\
        3.0 & 0.598300 & 1.992258 & 4.438638 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

\subsection{Ground state energy $r$ vs. $\mathcal E$}

    \begin{table}[h!]
    \caption{\label{tab:Ar-Ar} Ground state energy (in Ha) of the Ar-Ar system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 9.247342 & 9.110717 & 8.952432 \\
        1.0 & 2.981229 & 2.633184 & 2.076356 \\
        1.5 & 1.563464 & 0.829677 & -0.591543 \\
        2.0 & 1.023301 & -0.325559 & -2.992697 \\
        2.5 & 0.748161 & -1.377726 & -5.452778 \\
        3.0 & 0.590991 & -2.381467 & -7.976320 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Cs-Cs} Ground state energy (in Ha) of the Cs-Cs system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 4.076335 & 3.980857 & 3.863462 \\
        1.0 & 1.307214 & 1.035551 & 0.558141 \\
        1.5 & 0.673427 & 0.042066 & -1.194431 \\
        2.0 & 0.426306 & -0.786686 & -3.026094 \\
        2.5 & 0.296956 & -1.655817 & -5.032131 \\
        3.0 & 0.217699 & -2.584558 & -7.136808 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:H-H} Ground state energy (in Ha) of the H-H system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 3.757546 & 3.680220 & 3.584748 \\
        1.0 & 1.213930 & 0.994879 & 0.606484 \\
        1.5 & 0.649664 & 0.155212 & -0.841764 \\
        2.0 & 0.436524 & -0.467646 & -2.247426 \\
        2.5 & 0.330635 & -1.037533 & -3.672527 \\
        3.0 & 0.279296 & -1.563088 & -5.125057 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:He-He} Ground state energy (in Ha) of the He-He system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 4.838555 & 4.747673 & 4.637588 \\
        1.0 & 1.609674 & 1.370517 & 0.955271 \\
        1.5 & 0.928052 & 0.449201 & -0.551122 \\
        2.0 & 0.690066 & -0.067148 & -1.750946 \\
        2.5 & 0.597424 & -0.386765 & -2.715690 \\
        3.0 & 0.607965 & -0.544976 & -3.452658 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:K-K} Ground state energy (in Ha) of the K-K system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 3.900846 & 3.798718 & 3.672463 \\
        1.0 & 1.254074 & 0.961731 & 0.444593 \\
        1.5 & 0.646062 & -0.035078 & -1.362536 \\
        2.0 & 0.409452 & -0.892356 & -3.275553 \\
        2.5 & 0.286775 & -1.798818 & -5.377141 \\
        3.0 & 0.211508 & -2.769875 & -7.827196 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Kr-Kr} Ground state energy (in Ha) of the Kr-Kr system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 9.936548 & 9.795814 & 9.633507 \\
        1.0 & 3.196890 & 2.840242 & 2.274883 \\
        1.5 & 1.666467 & 0.914564 & -0.532113 \\
        2.0 & 1.078692 & -0.316154 & -3.056110 \\
        2.5 & 0.776461 & -1.455630 & -5.674813 \\
        3.0 & 0.599348 & -2.572968 & -8.404424 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Li-Li} Ground state energy (in Ha) of the Li-Li system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 2.989579 & 2.886101 & 2.754734 \\
        1.0 & 0.965106 & 0.657280 & 0.096843 \\
        1.5 & 0.498061 & -0.231815 & -1.636857 \\
        2.0 & 0.316132 & -1.061981 & -3.526222 \\
        2.5 & 0.223280 & -1.953835 & -5.616848 \\
        3.0 & 0.166518 & -2.914737 & -11.972520 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Ne-Ne} Ground state energy (in Ha) of the Ne-Ne system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 8.067324 & 7.938880 & 7.788706 \\
        1.0 & 2.648128 & 2.324114 & 1.795116 \\
        1.5 & 1.463214 & 0.814542 & -0.481886 \\
        2.0 & 1.037985 & -0.043649 & -2.342096 \\
        2.5 & 0.839105 & -0.668123 & -3.988911 \\
        3.0 & 0.769833 & -1.095276 & -5.406152 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Rb-Rb} Ground state energy (in Ha) of the Rb-Rb system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 4.031874 & 3.933375 & 3.812070 \\
        1.0 & 1.294297 & 1.013631 & 0.519442 \\
        1.5 & 0.666759 & 0.014231 & -1.261255 \\
        2.0 & 0.422361 & -0.828604 & -3.131122 \\
        2.5 & 0.294937 & -1.715198 & -5.181182 \\
        3.0 & 0.216807 & -2.663303 & -7.510481 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Xe-Xe} Ground state energy (in Ha) of the Xe-Xe system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
        \hline\\[-0.8em]
        0.5 & 10.472412 & 10.333027 & 10.172863 \\
        1.0 & 3.360994 & 3.008892 & 2.455036 \\
        1.5 & 1.743863 & 1.001161 & -0.421036 \\
        2.0 & 1.117696 & -0.272030 & -2.991068 \\
        2.5 & 0.792188 & -1.461408 & -5.680509 \\
        3.0 & 0.598300 & -2.651579 & -8.519189 \\
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{figure}[h!]
        \centering
            \includegraphics[scale=0.33]{plus_minus_coefs_tau0_r2_HH}
            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$. The purple dots correspond to the first 5 excited states of the H-H system for $r=2$ and $\mathcal E=0$.}
    \end{figure}

    \begin{figure}[h!]
        \centering
            \includegraphics[scale=0.33]{rational_tau0_r2_HH}
            \caption{\label{fig:rational} Plot of  $z=c^+_{20}(\epsilon, s(\epsilon))$ for the H-H system at $r=2$ and $\mathcal E=0$. The zeros are denoted by purple dots and correspond to the first excited states of the system.}
    \end{figure}
